### 2014-12-03 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edit to flow path table

\begin{table}[!ht]
\caption[Flow path related LODD/LODI incidents]
{Flow path related LODD/LODI incidents}
\begin{tabular}{lll}
\toprule
NIOSH Report No. & No. of LODDs/LODIs & Flow Path Details                                            \\
\midrule
99-F01   \cite{NIOSH:Pettit}        &  3 LODDs            &  From apartment into hallway on 10th     \\
                                    &                     &  floor of high-rise apartment building   \\
99-F21   \cite{NIOSH:Washenitz}     &  2 LODDs            &  Basement to 1st floor                   \\
                                    &  2 LODIs            &                                          \\
F2000-04 \cite{NIOSH:Mezzanotte}    &  3 LODDs            &  1st floor to 2nd floor                  \\
                                    &  3 civilian deaths  &                                          \\
F2000-16 \cite{NIOSH:McFall}        &  1 LODD             &  2nd floor hallway through               \\
                                    &  1 LODI             &  2nd floor apartment                     \\
                                    &  1 civilian death   &                                          \\
F2000-23 \cite{NIOSH:McFall2}       &  1 LODD             &  From ground level to 1st floor then to  \\
                                    &  2 LODIs            &  2nd floor, flow exited through ceiling  \\
F2000-43 \cite{NIOSH:McFall3}       &  1 serious LODI     &  1st floor to 2nd floor                  \\
                                    &  2 other LODIs      &                                          \\
F2004-02 \cite{NIOSH:Berardinelli}  &  1 LODD             &  1st floor to basement                   \\
F2005-02 \cite{NIOSH:Koedam}        &  1 LODD             &  Rear to front of the building           \\
                                    &  4 LODIs            &                                          \\
F2005-04 \cite{NIOSH:McFall4}       &  1 LODD             &  Basement to 1st floor                   \\
                                    &  9 LODIs            &                                          \\
F2007-09 \cite{NIOSH:Tarley}        &  1 LODD             &  3 story training burn - flow through    \\
                                    &  2 LODIs            &  all levels                              \\
F2007-35 \cite{NIOSH:Braddee}       &  4 LODIs            &  1st floor to 2nd floor                  \\
F2009-11 \cite{NIOSH:Merinar}       &  2 LODDs            &  Rear to front of the building           \\
F2011-13 \cite{NIOSH:Bowyer2}       &  2 LODDs            &  Lower level up stairs and through       \\
                                    &                     &  entry door and garage                   \\
F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartme  \\
F2012-28 \cite{NIOSH:Bowyer}        &  1 LODD             &  Attic fire extended into closed         \\
                                    &  1 LODI             &  porch and then into 2nd floor           \\
\bottomrule
\end{tabular}
\label{tab:LODD}
\end{table}

>>>>

\begin{table}[!ht]
\caption[Flow path related LODD/LODI incidents]
{Flow path related LODD/LODI incidents}
\begin{tabular}{lll}
\toprule
NIOSH Report No. & No. of LODDs/LODIs & Flow Path Details                                              \\
\midrule
99-F01   \cite{NIOSH:Pettit}        &  3 LODDs            &  From apartment into hallway on 10th       \\
                                    &                     &  floor of high-rise apartment building     \\
99-F21   \cite{NIOSH:Washenitz}     &  2 LODDs            &  Basement to 1st floor                     \\
                                    &  2 LODIs            &                                            \\
F2000-04 \cite{NIOSH:Mezzanotte}    &  3 LODDs            &  1st floor to 2nd floor                    \\
                                    &  3 civilian deaths  &                                            \\
F2000-16 \cite{NIOSH:McFall}        &  1 LODD             &  2nd floor hallway through                 \\
                                    &  1 LODI             &  2nd floor apartment                       \\
                                    &  1 civilian death   &                                            \\
F2000-23 \cite{NIOSH:McFall2}       &  1 LODD             &  From ground level to 1st floor then to    \\
                                    &  2 LODIs            &  2nd floor, flow exited through ceiling    \\
F2000-43 \cite{NIOSH:McFall3}       &  1 serious LODI     &  1st floor to 2nd floor                    \\
                                    &  2 other LODIs      &                                            \\
F2004-02 \cite{NIOSH:Berardinelli}  &  1 LODD             &  1st floor to basement                     \\
F2005-02 \cite{NIOSH:Koedam}        &  1 LODD             &  Rear to front of the building             \\
                                    &  4 LODIs            &                                            \\
F2005-04 \cite{NIOSH:McFall4}       &  1 LODD             &  Basement to 1st floor                     \\
                                    &  9 LODIs            &                                            \\
F2007-09 \cite{NIOSH:Tarley}        &  1 LODD             &  3 story training burn - flow through      \\
                                    &  2 LODIs            &  all levels                                \\
F2007-35 \cite{NIOSH:Braddee}       &  4 LODIs            &  1st floor to 2nd floor                    \\
F2009-11 \cite{NIOSH:Merinar}       &  2 LODDs            &  Rear to front of the building             \\
F2011-13 \cite{NIOSH:Bowyer2}       &  2 LODDs            &  Lower level up stairs and through         \\
                                    &                     &  entry door and garage                     \\
F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartment  \\
F2012-28 \cite{NIOSH:Bowyer}        &  1 LODD             &  Attic fire extended into closed           \\
                                    &  1 LODI             &  porch and then into 2nd floor             \\
\bottomrule
\end{tabular}
\label{tab:LODD}
\end{table}
